---
title: "Data Day Survey 2021"
author: "Dorcas Washington"
date: "12/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo=FALSE, warning=FALSE}
library(readxl)
#read in data
dat <- readxl::read_xlsx('Data Day survey responses.xlsx')

#relabeling the years
dat$yr2016 <- dat[,5]
dat$yr2017 <- dat[,6]
dat$yr2018 <- dat[,7]
dat$yr2019 <- dat[,8]
dat$yr2020 <- dat[,9]
dat$yr2021 <- dat[,10]

library(tidyverse)
library(dplyr)

#seperating the data set by attendence (attended or not)
dat2 <- dat %>% summarise(Attended2016 = sum(dat$yr2016=="Checked"), 
                          Attended2017 = sum(dat$yr2017=="Checked"),
                          Attended2018 = sum(dat$yr2018=="Checked"),
                          Attended2019 = sum(dat$yr2019=="Checked"),
                          Attended2020 = sum(dat$yr2020=="Checked"),
                          Attended2021 = sum(dat$yr2021=="Checked"))

# creating a frequency table by counts for those who attended
dat2_long <- pivot_longer(dat2, cols = starts_with("A"), names_to = "year", values_to="count" )

dat3 <- dat %>% summarise(NotAttended2016 = sum(dat$yr2016=="Unchecked"), 
                          NotAttended2017 = sum(dat$yr2017=="Unchecked"),
                          NotAttended2018 = sum(dat$yr2018=="Unchecked"),
                          NotAttended2019 = sum(dat$yr2019=="Unchecked"),
                         NotAttended2020 = sum(dat$yr2020=="Unchecked"),
                        NotAttended2021 = sum(dat$yr2021=="Unchecked"))


#frequency table of those who didn't attend (counts)
dat3_long <- pivot_longer(dat3, cols = starts_with("N"), names_to = "year", values_to="count")

library(ggplot2)

#frequency plot of those who attended
dat2_long$year<- c(2016:2021) 
ggplot(dat2_long) + geom_col(aes(x=year, y=count)) + theme_classic()



```
```{r, echo=FALSE, warning=FALSE}

# I'm converting all the NA's/Bot applicable to NA's in R
df <- sapply(dat, as.character)
convert_to_na <- function(x){
  val <- ifelse(x=="Not applicable", NA, x)
  as.factor(val)
}

# Converting list data into a data frame and using the above function to relabel 
# NA values

dat_new <- as.data.frame(lapply(df, convert_to_na))


# ggplot(dat_new, aes(x=`My.office.department.encourages.the.use.of.best.practices.in.data.use.and.management.`)) + geom_bar()
# 


# ggplot(dat, aes(x=`My office/department provides the resources or access to resources that I need to use best practices for data use and management.`)) + geom_bar()



```


```{r, echo=FALSE, warning=FALSE}
library(likert)



p1 <- dat_new[,12:24] %>% gather(name, value) %>% count(name, value)
p2 <- pivot_wider(p1, names_from = value, values_from = n)
p3 <- rowSums(cbind(p2$`Neutral or N/A`, p2$Neutral, p2$`NA`), na.rm = TRUE)

p2$`Neutral or N/A` <- p3

p2 <- p2[ ,-c(5,8)]
#rowSums(p2[,-1], na.rm = TRUE)
p4 <- likert::likert(Question ~., p2)


library(reshape2)
question_names <- paste0('Q',c(1:13))
p4$results$name <-question_names
group_order <- c('Strongly Agree', 'Agree', "Neutral or N/A", "Disagree", "Strongly Disagree")
results <- melt(p4$results, id.vars='name')

ymin <- 0
text.size <- 3

library(RColorBrewer)

ggplot(data = results, aes(x=name, y=value)) +  geom_bar(stat='identity', aes(fill=variable)) + labs(
        x = "Question",
        y = "Number of individuals")
```
Questions
Q1 "Attending.Data.Day.has.improved.the.way.I.work.with.students."                                                                    
Q2 "Data.Day.has.improved.my.network.within.the.UC.data.community."                                                                   
Q3 "Data.Day.taught.me.about.UC.resources.that.I.was.unaware.of.prior.to.the.event."                                                  
Q4 "I.have.made.changes.in.my.own.work.with.data.to.reflect.the.best.practices.learned.during.Data.Day."                              
Q5 "I.have.made.recommendations.or.suggestions.related.to.data.practices.to.colleagues.because.of.concepts.I.learned.during.Data.Day."

Q6 "I.have.made.recommendations.or.suggestions.related.to.data.practices.to.students.because.of.concepts.I.learned.during.Data.Day."  

Q7 "Most.of.my.colleagues.are.aware.of.Data.Day."                                                                                     
Q8 "Most.of.my.colleagues.have.attended.at.least.one.Data.Day.event.in.the.past."                                                     
Q9 "My.office.department.encourages.the.use.of.best.practices.in.data.use.and.management."             

Q10 "My.office.department.provides.the.resources.or.access.to.resources.that.I.need.to.use.best.practices.for.data.use.and.management."

Q11 "Overall, I.have.learned.a.lot.about.best.data.practices.because.of.attending.Data.Day.events."                  

Q12 "Please.name.the.resources.you.need.to.conduct.research.using.best.practices.that.the.University.is.not.providing." 

Q13 "The.University.of.Cincinnati.provides.all.the.resources.I.need.to.conduct.research.using.best.practices."  